### 2016-01-18 ch02-qlogms/excitation-design.tex
Small tweaks
Small changes

  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:misalignment-logms}
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

@@

  Now we can interpret \figref{fig:worstCaseBeta} in more detail.
  We see that for $\beta \in \set{0,1}$ (i.e. perfect alignment), the variance of a course grid (full lines) is lower than it is for a fine grid (dashed lines).
  This is to be expected as a coarse grid places more power at each individual line.
  Thereby it yields a smaller variance at those lines.
  It is better tailored to systems which are closely aligned to the excited frequency grid.
  However, there is a critical consequence: when there is a moderate misalignment $\beta$ of the system and the excitation grid, the variance will increase significantly and very fast.
  This effect is more important for lowly damped systems, as their $3\unit{dB}$ bandwidth is very narrow and hence their main response is easier to `miss'.

>>>>

  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:misalignment-logms}
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Intuitively, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

@@

  Now we can interpret \figref{fig:worstCaseBeta} in more detail.
  We see that for $\beta \in \set{0,1}$ (i.e. perfect alignment), the variance of a course grid (full lines) is lower than it is for a fine grid (dashed lines).
  This is to be expected as a coarse grid places more power at each individual line.
  Thereby it yields a smaller variance at those lines.
  It is better tailored to systems which are closely aligned to the excited frequency grid.
  However, there is a critical consequence: when there is a moderate misalignment $\beta$ of the system and the excitation grid, the variance increases significantly.
  This effect is more important for lightly-damped systems, as their $3\unit{dB}$ bandwidth is very narrow and hence their main response is easier to `miss'.
